An upper bound to gas delivery via pressure-swing adsorption in nanoporous materials

### 2020-05-11 gas-adsorption/gas-ads-body.tex
working through the paper and making edits and removing outdated comments.

\section{Introduction}
The transportation sector is dominantly powered by petroleum-based fuels \cite{davis2009transportation}. In the US, it is responsible for 36\% of energy-related carbon dioxide emissions \cite{useia} and 50,000 premature deaths per year associated with particulate matter and ozone emissions \cite{caiazzo2013air}. 
Natural gas and hydrogen (H$_2$) are alternative transportation fuels that emit fewer/less pollutants 
than petroleum-based fuels, and thus their widespread adoption could mitigate climate change 
\cite{mcglade2015geographical} and improve air quality for human health. Further, as the finite global 
petroleum resources are declining rapidly \cite{sorrell2010global}, the development of technologies for the widespread
adoption of sustainable transportation fuels, such as hydrogen, is critical.

Natural gas, mostly methane, is considered a transition (to a renewable and clean) fuel because 
it emits 25\% less carbon dioxide \cite{eia2013much} and less toxic 
byproducts \cite{wang2000full} upon combustion per unit energy produced compared to gasoline. From an 
economic standpoint, the supply of natural gas in the US is increasing as a result of hydraulic 
fracturing and horizontal drilling techniques \cite{usnatgassupply}. A positive environmental outlook 
for natural gas, however, is predicated on mitigating fugitive emissions (methane is itself a potent 
greenhouse gas) \cite{alvarez2012greater} and groundwater contamination \cite{osborn2011methane}
from hydraulic fracturing.

Hydrogen (H$_2$) is the ultimate transportation fuel because it emits only water when it electrochemically reacts with oxygen in a fuel cell to produce electricity and power a vehicle.
% Moreover, elemental hydrogen is very abundant, though bonded with oxygen (in water) or carbon (in hydrocarbons); H$_2$ does not occur naturally in abundant quantities.
Currently, hydrogen (H$_2$) is primarily produced by steam reforming of natural gas followed by the
water-gas shift reaction, which emits carbon dioxide \cite{crabtree2004hydrogen}. Notably, the 
environmental allure of hydrogen is predicated on its production via a renewable means, e.g.\ splitting
water using wind-generated electricity.

% \jordan{I got the values from wikipedia but the citation that wikipedia gave didn't link to the correct paper? Article is Energy Density.
% THIS PAPER says H2 at 700 bar is 4.7 MJ/L: Review on processing of metal–organic framework (MOF) materials towards system integration for hydrogen storage
% }
At ambient conditions, both methane
%(0.036 MJ/L)
and hydrogen gas
%(0.01 MJ/L)
possess a very low volumetric energy density compared to (liquid) gasoline.
%(34.2 MJ/L)
Consequently, under storage space constraints in passenger vehicles, natural gas and hydrogen must be densified for onboard storage to achieve a reasonable driving range on a ``full'' tank of fuel. Traditional densification approaches are liquefaction (cryogenic storage near atmospheric pressure)
% (at 1 atm, liquid CH$_4$ at 111~K to achieve 22.2 MJ/L~\cite{makal2012methane}, liquid H$_2$ at 20 K to achieve 8~MJ/L \cite{suh2011hydrogen})
or compression to high pressures (room temperature storage).
% (200 bar for CH$_4$ to achieve 9.2 MJ/L \cite{makal2012methane} and 700 bar for H$_2$ to achieve 4.5-5.3 MJ/L~\cite{unknown}).
Both approaches require expensive infrastructure at refilling stations and significant energy input; e.g., liquefaction of hydrogen consumes at least 30\% of its energy content~\cite{bossel2003energy}. Moreover, high-pressure storage tanks are heavy, thick-walled, and non-conformable, while cryogenic storage tanks are bulky, expensive, and afflicted by boil-off losses~\cite{hasan2009minimizing}.

>>>>

\section{Introduction}
The transportation sector is dominantly powered by petroleum-based
fuels~\cite{davis2009transportation}. In the United Sates, it is responsible
for 36\% of energy-related carbon dioxide emissions \cite{useia} and 50,000
premature deaths per year associated with particulate matter and ozone
emissions~\cite{caiazzo2013air}. Natural gas and hydrogen (H$_2$) are
alternative transportation fuels that emit fewer/less pollutants than
petroleum-based fuels, and thus their widespread adoption could mitigate
climate change~\cite{mcglade2015geographical} and improve air quality for human
health. Further, as the finite global petroleum resources are declining
rapidly~\cite{sorrell2010global}, the development of technologies for the
widespread adoption of sustainable transportation fuels, such as hydrogen, is
critical.

Natural gas, mostly methane, is considered a transition (to a renewable and
clean) fuel because it emits 25\% less carbon dioxide~\cite{eia2013much} and
fewer toxic byproducts~\cite{wang2000full} upon combustion per unit energy
produced compared to gasoline. From an economic standpoint, the supply of
natural gas in the United States is increasing as a result of hydraulic
fracturing and horizontal drilling techniques~\cite{usnatgassupply}. A positive
environmental outlook for natural gas, however, is predicated on mitigating
fugitive emissions (methane is itself a potent greenhouse
gas)~\cite{alvarez2012greater} and groundwater
contamination~\cite{osborn2011methane} from hydraulic fracturing.

Hydrogen (H$_2$) is the ultimate transportation fuel because it emits only
water when it electrochemically reacts with oxygen in a fuel cell to power a
vehicle. Currently, hydrogen (H$_2$) is primarily produced by steam reforming
of natural gas followed by the water-gas shift reaction, which emits carbon
dioxide \cite{crabtree2004hydrogen}. Notably, the environmental allure of
hydrogen is predicated on its production via a renewable means, e.g.\ splitting
water using wind-generated electricity.

At ambient conditions, both methane
%(0.036 MJ/L)
and hydrogen gas
%(0.01 MJ/L)
possess a very low volumetric energy density compared to (liquid) gasoline.
%(34.2 MJ/L)
Consequently, under storage space constraints in passenger vehicles, natural gas and hydrogen must be densified for onboard storage to achieve a reasonable driving range on a ``full'' tank of fuel. Traditional densification approaches are liquefaction (cryogenic storage near atmospheric pressure)
% (at 1 atm, liquid CH$_4$ at 111~K to achieve 22.2 MJ/L~\cite{makal2012methane}, liquid H$_2$ at 20 K to achieve 8~MJ/L \cite{suh2011hydrogen})
or compression to high pressures (room temperature storage).
% (200 bar for CH$_4$ to achieve 9.2 MJ/L \cite{makal2012methane} and 700 bar for H$_2$ to achieve 4.5-5.3 MJ/L~\cite{unknown}).
Both approaches require expensive infrastructure at refilling stations and significant energy input; e.g., liquefaction of hydrogen consumes at least 30\% of its energy content~\cite{bossel2003energy}. Moreover, high-pressure storage tanks are heavy, thick-walled, and non-conformable, while cryogenic storage tanks are bulky, expensive, and afflicted by boil-off losses~\cite{hasan2009minimizing}.
